### 2016-11-08 paper2.tex
Fixed labels

\subsection{Star Formation and Feedback}
Our suite of simulations use a range of different feedback
processes.  For all of the simulations shown in this paper, we use a common
star formation prescription.  Stars are formed at a rate proportional to the
local free-fall time of gas, such that
\begin{equation}
    \dot \rho_* = c_* \frac{\rho_{gas}}{t_{ff}}
    \label{sflaw}
\end{equation}
For each of these simulations, we used an efficiency parameter $c_* = 0.1$, the
value used by \citet{Stinson2013}.  Stars are allowed to form in a converging
flow when gas is cooler than $1.5\times10^4\; \rm{K}$, and with a density set to
that allowed by the gravity resolution, $\rho = M_{gas}/\epsilon^3 = 9.3\;
\rm{cm^{-3}}$.

@@

    \includegraphics[width=\textwidth]{figures2/stellar_image.eps}
    \caption[Mock stellar image of galaxy at z=0 with different feedback
    models]{Mock stellar image of each galaxy at $z=0$.  The top row shows the
    galaxies edge-on, while the bottom shows them face-on.  The no-feedback case
    shows very little disc, while the blastwave feedback case has a thin disc
    with a prominent bulge.  The superbubble galaxy appears nearly bulgeless,
    composed only of a truncated disc. Note also that the superbubble galaxy is
    bluer than the blastwave or no-feedback galaxies, evidence of a younger
    stellar population.}
    \label{stellar_image}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures2/column_density.eps}
    \caption[HI column density in a galaxy at z=0 with different feedback models]{HI
    column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse wisps.
    The two superbubble cases (especially with doubled supernova energy) have
    lofted a large amount of gas out of the disc, and some entrained dense
    clumps can be seen in this outflowing material.  The superbubble gas discs
    are much more flocculent than the blastwave disc, and where the feedback
    energy is doubled, the disc is strongly disrupted.}
    \label{column_density}
\end{figure}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures2/rotation_curve.eps}
    \caption[Rotation curves with different feedback models]{Rotation curves for
    each of our test cases.  As is clear, the superbubble cases have much lower
    central concentrations, giving a a rotation curve that rises to a flat
    $200\; \rm{km/s}$.  The peaked rotation curves in the cases with blastwave
    or no feedback are a result of their failure to remove low angular momentum
    gas at high redshift, giving bulge-dominated, centrally concentrated
    galaxies.}
    \label{rotation_curve}
\end{figure}

\section{Results}
\subsection{Redshift zero Disc Properties}
\begin{table}
    \scriptsize
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption[Halo Components at $z=0$ for different feedback models]{Halo
    components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the determined by the
    angular momentum of the stars (as detailed below).  All masses are in
    $M_\odot$.}
    \label{properties}
\end{table}

As can be seen in Figure~\ref{stellar_image}, the galaxy produced with

@@

    \label{circularity}

@@

    \label{mass_growth}

@@

    function of time/redshift.  As in figure~\ref{mass_growth}, only the

@@

    figure~\ref{mass_growth}, and here we also show, in the hatched region with

@@

    \label{stellar_fraction}

@@

    \label{sfr}

@@

    \label{burstiness}

@@

    \label{massloading}

@@

The gas component of this galaxy can be seen in Figure~\ref{column_density}.
The superbubble feedback is clearly much more effective at ejecting gas from the
disc, creating a halo of clumpy HI gas.  In the doubled feedback case, the disc
is heavily disrupted, with no spiral structure visible in either the stellar or
gas density images.  Thus the larger stellar disc is directly related to a more
extended gaseous disk.

The rotation curve in Figure~\ref{rotation_curve} shows that this ejection also
gives a flattened rotation curve without the central peak seen in simulations
with blastwave or no feedback.  This tells us that the mass distribution is much
less centrally concentrated when superbubble feedback is used, more evidence
that superbubble feedback is effective in preventing bulge formation.

One of the primary problems in older simulations was a much larger
bulge-to-total fraction based on a kinematic decomposition.  We adopt the same
kinematic decomposition as the original MUGS study.  We calculate, for each star
within the halo, a circularity parameter, which is simply the ratio of the
specific angular momentum component perpendicular to the disc ($j_z$) and the
specific angular momentum for a perfect circular orbit in the same potential
that the star sees $j_{circ}$.  As in the original MUGS study, we identify bulge
stars as having $j_z/j_{circ} < 0.7$ and orbital radii of $< 5\; \rm{kpc}$.  We
find, using these criteria, that our fiducial B/T ratio at $z=0$ is 0.09,
slightly smaller than the Milky Way's $\sim0.14$, and greatly reduced compared
to the 0.55 found in the original MUGS paper, and well within the observational
constraints from \citet{Allen2006}.  As these numbers, and the distribution of
this circularity parameter found in Figure~\ref{circularity} show, the vigorous
expulsion of central gas with superbubble feedback is a powerful bulge
prevention and destruction mechanism.  Each of the 13 samples from the Aquila
project \citep{Scannapieco2012} suffered from either from a bulge-dominated
stellar circularity profile, or from a massively peaked (or in some cases simply
too high) rotation curve.  Even the three cases that managed to produce a
reasonable stellar mass fraction (each of these generated strong outflows,
either through SMBH feedback or wind decoupling) still failed to produce
disc-dominated galaxies.  Of their sample, only four cases had more than 40\% of
the stellar mass in disc stars, but all of these cases massively overproduced
stars.

@@

Of what remain, only 29\% of the baryonic mass in the superbubble galaxy disc is
in stars, compared to 63\% in the blastwave galaxy, and 89\% in the no
feedback galaxy.  The basic properties of each halo can be found in
table~\ref{properties}.

\subsection{Halo Evolution and Star Formation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux}
\end{figure}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth}
and~\ref{stellar_fraction} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching relation at $z\sim3$ for the blastwave, and before
$z=5$ without feedback, giving galaxies that lie above the abundance-matching
relationships over nearly their entire history and mass evolution.  With
superbubble feedback, this galaxy lies within the range of observed stellar
masses over its entire evolution, although on the low side of this range at low
redshift.  Arbitrarily increasing feedback energies, despite having reasonable
star formation rates near $z=0$, under produces stars for most cosmic history,
giving stellar masses {\it lower} than predicted by abundance matching.  Stellar
and total masses were calculated for the region inside $R_{vir}$.  As the halo
grows over time, brief reductions in the stellar mass fraction can be seen for
the no-feedback and blastwave feedback halos in Figure~\ref{stellar_fraction},
simply by the accretion of gas and dark matter that has not yet made it to the
galaxy disc.  Once these mergers complete, the stellar fraction rate leaps up
once again because of the new supply of gas.  The relative flatness in this
figure at low redshift is reflected in the relative flatness in the star
formation rate, shown in figure~\ref{sfr}.  This is simply a side effect of the
massive star formation rates at high redshift:  the bulk of star forming gas has
been consumed, and thus star formation has slowed.

The star formation rate, in bins of $150\: \rm{Myr}$, is shown in
Figure~\ref{sfr}.  With no feedback, or blastwave feedback, star formation is
extremely vigorous before $z=2$, slowing at low redshift as gas available for
star formation is exhausted.  With superbubble feedback, star formation is
relatively constant over nearly the entire history of the halo, with only a
gradual increase towards $z=0$.  This apparent quiescence is a function of the
large time window over which we are averaging our star formation rate.  In
Figure~\ref{burstiness}, you can see clearly that despite having an average star
formation rate of $\sim1\; \rm{M_\odot yr^{-1}}$, this is punctuated by bursts
of star formation of as much as $\sim10\; \rm{M_\odot yr^{-1}}$.  Very similar
results were seen in \citet{Muratov2015}, where bursts of star formation are
followed by peaks in the outflow rates.  This burstiness is a important if
stellar feedback is to drive galactic winds:  to generate large superbubbles,
star formation must be clustered in both space and time.  Whether these bursts
of star formation are able to effectively remove baryons from the disc
ultimately depends on the mass loading of the winds that they drive.

\subsection{Outflow Analysis}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_outflow.eps}
    \caption[High redshift winds remove low angular momentum gas]{High-redshift
    winds preferentially remove low angular momentum material.  As can be seen
    here, significantly more low angular momentum material is removed by
    superbubble feedback than by the weaker blastwave feedback, but the amount
    of ejected high-angular momentum material is roughly equal.}
        \label{angular_momentum_outflow}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/phase.eps}
    \caption[Gas phase diagram for g1536]{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas
        with temperatures above $10^5\;K$ contains roughly 40\% of the gas mass
        in the halo.  This gas is a mixture of virial-shocked pristine gas,
        which has never been within the interior $0.1R_{vir}$, and outflowing
        material ejected from the galaxy.  This buoyant, high-entropy gas exits
        the galaxy at high temperature, and cools adiabatically as it rises
        through the CGM.  The three colored contours show the major components
        of this hot coronal gas.  Pristine gas, never falling within the
        interior, is shown in blue.  Young superbubbles, not yet having broken out
        of the galaxy, are shown in red.  Outflowing material that was once inside the
        galaxy but is now cooling adiabatically as it rises through the CGM can be seen
        in orange.  The contours show the 1.5\%, 1\%, and 0.5\% levels for the
        total mass in each cut.}
        \label{phase}
\end{figure}
Star formation in the disc drives hot, fast-moving outflows from the central star
forming regions.  These outflows have temperatures of $\sim2\times10^7\; \rm{K}$
as they leave the disc, and also entrain some cold material with them.
Typically outflow velocities are a few hundred $\rm{km/s}$, less than the
escape velocity of the halo, but sufficient to propel gas to large radii before
it begins to fall in again.

We calculated inflow and outflow rates and velocities by examining particles
within a spherical shell, with inner radius $0.1R_{vir}$ and outer radius
$R_{vir}$ (giving a shell of thickness $0.9R_{vir}$).  We use the $\bar\rho =
200\rho_{crit}$ definition for $R_{vir}$.  Particles with $v_r < 0$ are
inflowing, while those with $v_r > 0$ are outflowing.
Within this shell, the mass flux is determined simply as:
\begin{equation}
    \dot M = \sum_{r_i\in\mathrm{shell}}\frac{M_i v_i}{0.9R_{vir}}
    \label{halo_massflux}
\end{equation}

As figure~\ref{massloading} shows, the outflow behavior of this galaxy is
fundamentally different when superbubble feedback is used.  The wind mass
loading factor $\eta = \dot M_{outflow} / \dot M_*$, a measure of how
efficiently feedback is generating outflows, is roughly an order of magnitude
larger during the bursts of star formation from $z=4-2$, expelling a large
amount of gas from the disc early on.  The resulting suppression of
high-redshift star formation is key to obtaining the correct stellar mass
relation as the halo grows, is unmistakable in figure~\ref{mass_growth}
and~\ref{stellar_fraction}.  Evidence of these outflows can be seen in the $z=0$
column density images in figure~\ref{column_density}.  High-latitude neutral
hydrogen from both ejected and infalling material can be seen in the two
superbubble cases, but is totally absent otherwise.  The smaller amount seen
around the high feedback energy case is simply due to this gas being expelled
further.  The reason superbubbles are so effective at removing mass from the
galaxy and thus regulating the stellar mass depends both on the higher outflow
rates as well as the lower star formation rates needed to drive these outflows,
leading to much larger mass loading factors than the blastwave model can
achieve.  This is clearly shown in figure~\ref{massloading}, as the top panel is
essentially the middle panel divided by the bottom panel.  The outflow rates
driven by superbubbles is at most $\sim2$ times greater than the blastwave model,
but since this is driven by a comparatively tiny amount of star formation, the
massloading, $\eta$, is nearly 10 times greater at high redshift.  The factor of
$\sim2$ higher outflow rate is what we would expect from the roughly $\sim2$
larger baryon depletion from the superbubble vs. blastwave cases.

The effectiveness of the superbubble-driven galactic winds can be clearly seen
in figure~\ref{net_accretion}, where the net accretion of stars and gas is
greatly reduced by the use of superbubble feedback, resulting at $z=1$ in a net
reduction in the total baryonic mass inside $0.5R_{vir}$ of $\sim14\%$ vs.
blastwave feedback, and $\sim30\%$ vs. no feedback whatsoever (along with the 
removal of baryons from the disc discussed earlier. As the outflow
rate drops towards $z=0$, much of this ejected material falls back onto the
disc, and the outflows transition to a fountain mode, actually increasing
the inflow rate seen compared to the blastwave feedback case in
figure~\ref{inflow_outflow}.  This increase in the accretion of gas fuels an
equivalent increase in star formation, as is seen in figures~\ref{sfr}
and~\ref{massloading}.

Figure~\ref{angular_momentum_netflux} shows that the total accreted gas switches
from being dominated by low angular momentum material to being primarily high
angular momentum material at $z\approx2$.  Because $\eta$ is high ($\sim 10$)
during this period, low-angular momentum material is preferentially ejected from
the galaxy without forming a significant number of stars.  These results agree
quite well with the results of \citet{Muratov2015}, which also found $L^*$
progenitors at $z>2$ had wind mass loadings $\eta\sim 10$. The preferential
ejection of low angular momentum gas is clear in
figure~\ref{angular_momentum_outflow}.  The small amount of high angular
momentum material accreted before $z=1$ is ejected at an essentially equal rate
with or without superbubble-driven winds, but low angular momentum material is
propelled into winds at roughly twice the rate when superbubble feedback is
taken into account.

The phase diagram in figure~\ref{phase} shows that, as expected, the galaxy
contains both a hot halo (in which nearly half of the gas mass can be found),
and contains no gas in regions of short cooling time.  This behavior was shown
previously in the isolated galaxy simulations of \citet{Keller2014}.  The hot
halo gas can be divided into three major components. The coolest component is
pristine, virial shocked material that has not ever been accreted (never passed
within $0.1R_{vir}$ of the halo center).  The hottest gas is actually not yet in
the corona, but is the interior of young superbubbles still within the galaxy
disc.  As this material leaves the disc, it cools adiabatically in the lower
pressure environment of the halo, as can be seen in from the $\rho^{2/3}$
adiabatic path it takes through the phase diagram.  Detailed analysis of this
halo gas, especially in comparison to observations like those of
\citet{Steidel2010}, will be explored in a future study of a larger sample of
L* galaxies.

>>>>

\subsection{Star Formation and Feedback}
Our suite of simulations use a range of different feedback
processes.  For all of the simulations shown in this paper, we use a common
star formation prescription.  Stars are formed at a rate proportional to the
local free-fall time of gas, such that
\begin{equation}
    \dot \rho_* = c_* \frac{\rho_{gas}}{t_{ff}}
    \label{sflaw2}
\end{equation}
For each of these simulations, we used an efficiency parameter $c_* = 0.1$, the
value used by \citet{Stinson2013}.  Stars are allowed to form in a converging
flow when gas is cooler than $1.5\times10^4\; \rm{K}$, and with a density set to
that allowed by the gravity resolution, $\rho = M_{gas}/\epsilon^3 = 9.3\;
\rm{cm^{-3}}$.

@@

    \includegraphics[width=\textwidth]{figures2/stellar_image.eps}
    \caption[Mock stellar image of galaxy at z=0 with different feedback
    models]{Mock stellar image of each galaxy at $z=0$.  The top row shows the
    galaxies edge-on, while the bottom shows them face-on.  The no-feedback case
    shows very little disc, while the blastwave feedback case has a thin disc
    with a prominent bulge.  The superbubble galaxy appears nearly bulgeless,
    composed only of a truncated disc. Note also that the superbubble galaxy is
    bluer than the blastwave or no-feedback galaxies, evidence of a younger
    stellar population.}
    \label{stellar_image2}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures2/column_density.eps}
    \caption[HI column density in a galaxy at z=0 with different feedback models]{HI
    column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse wisps.
    The two superbubble cases (especially with doubled supernova energy) have
    lofted a large amount of gas out of the disc, and some entrained dense
    clumps can be seen in this outflowing material.  The superbubble gas discs
    are much more flocculent than the blastwave disc, and where the feedback
    energy is doubled, the disc is strongly disrupted.}
    \label{column_density2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures2/rotation_curve.eps}
    \caption[Rotation curves with different feedback models]{Rotation curves for
    each of our test cases.  As is clear, the superbubble cases have much lower
    central concentrations, giving a a rotation curve that rises to a flat
    $200\; \rm{km/s}$.  The peaked rotation curves in the cases with blastwave
    or no feedback are a result of their failure to remove low angular momentum
    gas at high redshift, giving bulge-dominated, centrally concentrated
    galaxies.}
    \label{rotation_curve2}
\end{figure}

\section{Results}
\subsection{Redshift zero Disc Properties}
\begin{table}
    \scriptsize
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption[Halo Components at $z=0$ for different feedback models]{Halo
    components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the determined by the
    angular momentum of the stars (as detailed below).  All masses are in
    $M_\odot$.}
    \label{properties2}
\end{table}

As can be seen in Figure~\ref{stellar_image2}, the galaxy produced with

@@

    \label{circularity2}

@@

    \label{mass_growth2}

@@

    function of time/redshift.  As in figure~\ref{mass_growth2}, only the

@@

    figure~\ref{mass_growth2}, and here we also show, in the hatched region with

@@

    \label{stellar_fraction2}

@@

    \label{sfr2}

@@

    \label{burstiness2}

@@

    \label{massloading2}

@@

The gas component of this galaxy can be seen in Figure~\ref{column_density2}.
The superbubble feedback is clearly much more effective at ejecting gas from the
disc, creating a halo of clumpy HI gas.  In the doubled feedback case, the disc
is heavily disrupted, with no spiral structure visible in either the stellar or
gas density images.  Thus the larger stellar disc is directly related to a more
extended gaseous disk.

The rotation curve in Figure~\ref{rotation_curve2} shows that this ejection also
gives a flattened rotation curve without the central peak seen in simulations
with blastwave or no feedback.  This tells us that the mass distribution is much
less centrally concentrated when superbubble feedback is used, more evidence
that superbubble feedback is effective in preventing bulge formation.

One of the primary problems in older simulations was a much larger
bulge-to-total fraction based on a kinematic decomposition.  We adopt the same
kinematic decomposition as the original MUGS study.  We calculate, for each star
within the halo, a circularity parameter, which is simply the ratio of the
specific angular momentum component perpendicular to the disc ($j_z$) and the
specific angular momentum for a perfect circular orbit in the same potential
that the star sees $j_{circ}$.  As in the original MUGS study, we identify bulge
stars as having $j_z/j_{circ} < 0.7$ and orbital radii of $< 5\; \rm{kpc}$.  We
find, using these criteria, that our fiducial B/T ratio at $z=0$ is 0.09,
slightly smaller than the Milky Way's $\sim0.14$, and greatly reduced compared
to the 0.55 found in the original MUGS paper, and well within the observational
constraints from \citet{Allen2006}.  As these numbers, and the distribution of
this circularity parameter found in Figure~\ref{circularity2} show, the vigorous
expulsion of central gas with superbubble feedback is a powerful bulge
prevention and destruction mechanism.  Each of the 13 samples from the Aquila
project \citep{Scannapieco2012} suffered from either from a bulge-dominated
stellar circularity profile, or from a massively peaked (or in some cases simply
too high) rotation curve.  Even the three cases that managed to produce a
reasonable stellar mass fraction (each of these generated strong outflows,
either through SMBH feedback or wind decoupling) still failed to produce
disc-dominated galaxies.  Of their sample, only four cases had more than 40\% of
the stellar mass in disc stars, but all of these cases massively overproduced
stars.

@@

Of what remain, only 29\% of the baryonic mass in the superbubble galaxy disc is
in stars, compared to 63\% in the blastwave galaxy, and 89\% in the no
feedback galaxy.  The basic properties of each halo can be found in
table~\ref{properties2}.

\subsection{Halo Evolution and Star Formation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux2}
\end{figure}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth2}
and~\ref{stellar_fraction2} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching relation at $z\sim3$ for the blastwave, and before
$z=5$ without feedback, giving galaxies that lie above the abundance-matching
relationships over nearly their entire history and mass evolution.  With
superbubble feedback, this galaxy lies within the range of observed stellar
masses over its entire evolution, although on the low side of this range at low
redshift.  Arbitrarily increasing feedback energies, despite having reasonable
star formation rates near $z=0$, under produces stars for most cosmic history,
giving stellar masses {\it lower} than predicted by abundance matching.  Stellar
and total masses were calculated for the region inside $R_{vir}$.  As the halo
grows over time, brief reductions in the stellar mass fraction can be seen for
the no-feedback and blastwave feedback halos in Figure~\ref{stellar_fraction2},
simply by the accretion of gas and dark matter that has not yet made it to the
galaxy disc.  Once these mergers complete, the stellar fraction rate leaps up
once again because of the new supply of gas.  The relative flatness in this
figure at low redshift is reflected in the relative flatness in the star
formation rate, shown in figure~\ref{sfr2}.  This is simply a side effect of the
massive star formation rates at high redshift:  the bulk of star forming gas has
been consumed, and thus star formation has slowed.

The star formation rate, in bins of $150\: \rm{Myr}$, is shown in
Figure~\ref{sfr2}.  With no feedback, or blastwave feedback, star formation is
extremely vigorous before $z=2$, slowing at low redshift as gas available for
star formation is exhausted.  With superbubble feedback, star formation is
relatively constant over nearly the entire history of the halo, with only a
gradual increase towards $z=0$.  This apparent quiescence is a function of the
large time window over which we are averaging our star formation rate.  In
Figure~\ref{burstiness2}, you can see clearly that despite having an average star
formation rate of $\sim1\; \rm{M_\odot yr^{-1}}$, this is punctuated by bursts
of star formation of as much as $\sim10\; \rm{M_\odot yr^{-1}}$.  Very similar
results were seen in \citet{Muratov2015}, where bursts of star formation are
followed by peaks in the outflow rates.  This burstiness is a important if
stellar feedback is to drive galactic winds:  to generate large superbubbles,
star formation must be clustered in both space and time.  Whether these bursts
of star formation are able to effectively remove baryons from the disc
ultimately depends on the mass loading of the winds that they drive.

\subsection{Outflow Analysis}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_outflow.eps}
    \caption[High redshift winds remove low angular momentum gas]{High-redshift
    winds preferentially remove low angular momentum material.  As can be seen
    here, significantly more low angular momentum material is removed by
    superbubble feedback than by the weaker blastwave feedback, but the amount
    of ejected high-angular momentum material is roughly equal.}
        \label{angular_momentum_outflow2}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/phase.eps}
    \caption[Gas phase diagram for g1536]{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas
        with temperatures above $10^5\;K$ contains roughly 40\% of the gas mass
        in the halo.  This gas is a mixture of virial-shocked pristine gas,
        which has never been within the interior $0.1R_{vir}$, and outflowing
        material ejected from the galaxy.  This buoyant, high-entropy gas exits
        the galaxy at high temperature, and cools adiabatically as it rises
        through the CGM.  The three colored contours show the major components
        of this hot coronal gas.  Pristine gas, never falling within the
        interior, is shown in blue.  Young superbubbles, not yet having broken out
        of the galaxy, are shown in red.  Outflowing material that was once inside the
        galaxy but is now cooling adiabatically as it rises through the CGM can be seen
        in orange.  The contours show the 1.5\%, 1\%, and 0.5\% levels for the
        total mass in each cut.}
        \label{phase2}
\end{figure}
Star formation in the disc drives hot, fast-moving outflows from the central star
forming regions.  These outflows have temperatures of $\sim2\times10^7\; \rm{K}$
as they leave the disc, and also entrain some cold material with them.
Typically outflow velocities are a few hundred $\rm{km/s}$, less than the
escape velocity of the halo, but sufficient to propel gas to large radii before
it begins to fall in again.

We calculated inflow and outflow rates and velocities by examining particles
within a spherical shell, with inner radius $0.1R_{vir}$ and outer radius
$R_{vir}$ (giving a shell of thickness $0.9R_{vir}$).  We use the $\bar\rho =
200\rho_{crit}$ definition for $R_{vir}$.  Particles with $v_r < 0$ are
inflowing, while those with $v_r > 0$ are outflowing.
Within this shell, the mass flux is determined simply as:
\begin{equation}
    \dot M = \sum_{r_i\in\mathrm{shell}}\frac{M_i v_i}{0.9R_{vir}}
    \label{halo_massflux2}
\end{equation}

As figure~\ref{massloading2} shows, the outflow behavior of this galaxy is
fundamentally different when superbubble feedback is used.  The wind mass
loading factor $\eta = \dot M_{outflow} / \dot M_*$, a measure of how
efficiently feedback is generating outflows, is roughly an order of magnitude
larger during the bursts of star formation from $z=4-2$, expelling a large
amount of gas from the disc early on.  The resulting suppression of
high-redshift star formation is key to obtaining the correct stellar mass
relation as the halo grows, is unmistakable in figure~\ref{mass_growth2}
and~\ref{stellar_fraction2}.  Evidence of these outflows can be seen in the $z=0$
column density images in figure~\ref{column_density2}.  High-latitude neutral
hydrogen from both ejected and infalling material can be seen in the two
superbubble cases, but is totally absent otherwise.  The smaller amount seen
around the high feedback energy case is simply due to this gas being expelled
further.  The reason superbubbles are so effective at removing mass from the
galaxy and thus regulating the stellar mass depends both on the higher outflow
rates as well as the lower star formation rates needed to drive these outflows,
leading to much larger mass loading factors than the blastwave model can
achieve.  This is clearly shown in figure~\ref{massloading2}, as the top panel is
essentially the middle panel divided by the bottom panel.  The outflow rates
driven by superbubbles is at most $\sim2$ times greater than the blastwave model,
but since this is driven by a comparatively tiny amount of star formation, the
massloading, $\eta$, is nearly 10 times greater at high redshift.  The factor of
$\sim2$ higher outflow rate is what we would expect from the roughly $\sim2$
larger baryon depletion from the superbubble vs. blastwave cases.

The effectiveness of the superbubble-driven galactic winds can be clearly seen
in figure~\ref{net_accretion2}, where the net accretion of stars and gas is
greatly reduced by the use of superbubble feedback, resulting at $z=1$ in a net
reduction in the total baryonic mass inside $0.5R_{vir}$ of $\sim14\%$ vs.
blastwave feedback, and $\sim30\%$ vs. no feedback whatsoever (along with the 
removal of baryons from the disc discussed earlier. As the outflow
rate drops towards $z=0$, much of this ejected material falls back onto the
disc, and the outflows transition to a fountain mode, actually increasing
the inflow rate seen compared to the blastwave feedback case in
figure~\ref{inflow_outflow2}.  This increase in the accretion of gas fuels an
equivalent increase in star formation, as is seen in figures~\ref{sfr2}
and~\ref{massloading2}.

Figure~\ref{angular_momentum_netflux2} shows that the total accreted gas switches
from being dominated by low angular momentum material to being primarily high
angular momentum material at $z\approx2$.  Because $\eta$ is high ($\sim 10$)
during this period, low-angular momentum material is preferentially ejected from
the galaxy without forming a significant number of stars.  These results agree
quite well with the results of \citet{Muratov2015}, which also found $L^*$
progenitors at $z>2$ had wind mass loadings $\eta\sim 10$. The preferential
ejection of low angular momentum gas is clear in
figure~\ref{angular_momentum_outflow2}.  The small amount of high angular
momentum material accreted before $z=1$ is ejected at an essentially equal rate
with or without superbubble-driven winds, but low angular momentum material is
propelled into winds at roughly twice the rate when superbubble feedback is
taken into account.

The phase diagram in figure~\ref{phase2} shows that, as expected, the galaxy
contains both a hot halo (in which nearly half of the gas mass can be found),
and contains no gas in regions of short cooling time.  This behavior was shown
previously in the isolated galaxy simulations of \citet{Keller2014}.  The hot
halo gas can be divided into three major components. The coolest component is
pristine, virial shocked material that has not ever been accreted (never passed
within $0.1R_{vir}$ of the halo center).  The hottest gas is actually not yet in
the corona, but is the interior of young superbubbles still within the galaxy
disc.  As this material leaves the disc, it cools adiabatically in the lower
pressure environment of the halo, as can be seen in from the $\rho^{2/3}$
adiabatic path it takes through the phase diagram.  Detailed analysis of this
halo gas, especially in comparison to observations like those of
\citet{Steidel2010}, will be explored in a future study of a larger sample of
L* galaxies.
